HMM Model development

### 2020-05-07 dev/hmm_model_devel.Rmd
A slightly better observational model

```{r}
data <- hmm_simulator(10, 20, 2)

@@

data <- hmm_simulator(10, 20, 2)

if(inherits(model, "stanmodel")) {
  fit <- sampling(model, data = data$observed, control = list(adapt_delta = adapt_delta))
} else {
  cmdstan_fit <- model$sample(data = data$observed, adapt_delta = adapt_delta)
  fit <- rstan::read_stan_csv(cmdstan_fit$output_files())
}
evaluation_summary(fit, data$true)

@@

```{r}
sbc_res <- sbc(model, generator = function() {hmm_simulator(10, 20, 2) }, N_steps = 100, control = list(adapt_delta = adapt_delta))

@@

>>>>

```{r}
data <- hmm_simulator(10, 20, 2, use_noisy_states = FALSE)

@@

data <- hmm_simulator(10, 20, 2, use_noisy_states = TRUE)

if(inherits(model, "stanmodel")) {
  fit <- sampling(model, data = data$observed, control = list(adapt_delta = adapt_delta), chains = 1)
} else {
  cmdstan_fit <- model$sample(data = data$observed, adapt_delta = adapt_delta)
  fit <- rstan::read_stan_csv(cmdstan_fit$output_files())
}
evaluation_summary(fit, data$true)

@@

```{r}
sbc_res <- sbc(model, generator = function() {hmm_simulator(10, 20, 2, use_noisy_states = TRUE) }, N_steps = 100, control = list(adapt_delta = adapt_delta))

@@

```{r}
library(brms)
test_data <- data.frame(a = c(1,2,3), b = c(0.5,1.0,1.5), x1 = c("A"), x2 = c(0,1,2))
f <- cbind(a,b) ~ 0 + (0 + x2 | a | x1)
make_stancode(f, data = test_data)
make_standata(f, data = test_data)
```
